Unveiling Toronto's Respiratory Landscape

### 2024-01-25 outputs/paper/paper.qmd
Update paper.qmd

# Plotting
ggplot(filtered_data_2023, aes(x = `Type of Outbreak`, fill = `Type of Outbreak`)) +
  geom_bar() +
  labs(title = "Reports of Respiratory Outbreaks in Toronto Healthcare Institutions (2023)",
       x = "Type of Outbreak",
       y = "Count") +
  theme_minimal()
```
## Prevalence of Respiratory Infections
The analysis of respiratory infection trends in the aftermath of the COVID-19 pandemic reveals a noticeable increase in the overall prevalence of respiratory infections throughout the year 2023, presenting a distinct contrast with the preceding year, 2020. This notable rise extends beyond pre-pandemic norms, signifying a substantial transformation in the landscape of respiratory health, as highlighted in (@Maison). Consequently, there is a compelling need for an in-depth exploration of potential contributing factors and the development of adaptive public health strategies to effectively address the evolving challenges within the realm of respiratory infections.

>>>>

# Plotting
ggplot(filtered_data_2023, aes(x = `Type of Outbreak`, fill = `Type of Outbreak`)) +
  geom_bar() +
  labs(title = "Reports of Respiratory Outbreaks (2023)",
       x = "Type of Outbreak",
       y = "Count") +
  theme_minimal()
```
## Prevalence of Respiratory Infections
The analysis of respiratory infection trends in the aftermath of the COVID-19 pandemic reveals a noticeable increase in the overall prevalence of respiratory infections throughout the year 2023, presenting a distinct contrast with the preceding year, 2020. This notable rise extends beyond pre-pandemic norms, signifying a substantial transformation in the landscape of respiratory health, as highlighted in (@Maison). Consequently, there is a compelling need for an in-depth exploration of potential contributing factors and the development of adaptive public health strategies to effectively address the evolving challenges within the realm of respiratory infections.
